---
title: "`r title()` Mature Inventory Assessment"
author: "Forest Analysis and Inventory Branch"
date: "Version 2025-04-22; Created `r Sys.Date()`"
#runtime: shiny
always_allow_html: true
geometry: margin=1cm
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    toc: true
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::opts_chunk$set(fig.height = 4, collapse = TRUE)
knitr::opts_chunk$set(dev = "ragg_png")
set_flextable_defaults(fonts_ignore=TRUE)

htmltopdf <-function(x) {
  if (input$format == "HTML"){
    x
    } else {
      pandoc::pandoc_convert(text = x, from = "html", to = "markdown")
      }
}

colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}
```

<style>
.leaflet {
    margin: auto;
}
</style>


## Overview

`r htmltopdf(description())`

```{r samplemap, fig.width=8, echo=FALSE, fig.align='center'}
samplemap()
```

<br>


## Summary of Key Results

#### Sample Size & Measurement Year by Ground Sample Design

```{r samplesize, echo=FALSE,warning=FALSE, message = FALSE}
samplesize()
```


::: columns
::: column

#### Leading Species Agreement (Inventory vs. Ground)

```{r, include=T, echo=F,warning=FALSE, message = FALSE}
correct_sp_lead()
```
:::

::: column

#### Overall Species Agreement (Inventory vs. Ground)

```{r, include=T, echo=F,warning=FALSE, message = FALSE}
corsp_vol_flex()
```
:::
:::

#### Listing of those Attributes where Ground: Inventory ratio of means are practically different (Y) or not practically different (N) from 1.0. Attributes which are not listed here have inconclusive (I) results.

::: columns
::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
test1()

test2()

test3()
```
:::

::: column
```{r, include=T, fig.height=8,fig.width=3,echo=F,warning=FALSE}
fig2()
```
:::
:::

## Stand Summaries

`r htmltopdf(ysd())`

```{r, include=T, fig.height=8,echo=F,warning=FALSE}
table1()

table2()

table3()

table4()
```

## Componets of Bias

#### Model vs. Attribute Bias

`r htmltopdf(bias_comp())`

```{r, fig.width=8,fig.height=3, echo=FALSE,warning=FALSE, message = FALSE}
fig3() + theme_bw(12) +
      theme(
        legend.position = "top",
          axis.ticks = element_blank(),
          axis.text.y = element_blank(),
          panel.grid.major.y = element_blank(),
          #panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          strip.placement = "outside"
      ) 

```

::: columns
::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
fig3_1()
```
:::

::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
fig3_2()
```
:::
:::


## Ground vs. Inventory

#### Leading Species

`r htmltopdf(spcomp_text())`

```{r, fig.height=4,echo=FALSE,warning=FALSE}
ld_table1() %>% bg(j = (1:(ld_table1()$body$content$ncol/2))*2, 
                     bg = "lightgray", part = "body")

ld_table2() %>% bg(j = (1:(ld_table2()$body$content$ncol/2))*2, 
                     bg = "lightgray", part = "body")

```

#### Overall Species

```{r, fig.height=4,echo=FALSE,warning=FALSE}
fig4() + theme_bw(12) +
    theme(
      panel.grid.major.y = element_line(color = 'darkgray'), 
      plot.caption = element_text(hjust=0, size=rel(1.2)),
      legend.position="top",
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )  

fig5() + theme_bw(12) +
    theme(
      panel.grid.major.y = element_line(color = 'darkgray'), 
      plot.caption = element_text(hjust=0, size=rel(1.2)),
      legend.position="top",
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )  

```

#### Other Attributes

```{r, fig.height=8,echo=FALSE,warning=FALSE}
fig6() + theme_bw(12) +
    theme(
       strip.background.x = element_rect(fill=NA, colour=NA,size=1)
    )  

```


## Inventory Standards of Data Collection

`r htmltopdf(stdcode_text())`

```{r, fig.height=2,echo=FALSE,warning=FALSE}
fig7() + theme_bw(12) +
    theme(
      legend.title = NULL,
          rect = element_blank(),
          panel.grid.major.y = element_blank()
    )  
```


## Wildfire Impact

#### Ground Samples Impacted by Recent Wildfires

`r htmltopdf(fire_text())`

```{r, fig.width=5, fig.height=3,echo=FALSE,warning=FALSE, message = FALSE}
fig8() 
```

```{r firemap, fig.width=8, echo=FALSE, fig.align='center'}
firemap()
```


## Forest Health

#### Growth and Mortality

`r htmltopdf(coctext())`

```{r, fig.height=4,echo=FALSE,warning=FALSE, message = FALSE}
cocfig() + theme_bw(12) +
      theme(
        axis.title.y = element_text(color="steelblue"),
        axis.title.y.right = element_text(colour = "#B4464B"),
        legend.box.background = element_rect(fill = "white", color = NA),
        legend.position = c(0.15, 0.85),
        legend.title = element_blank(),
        axis.line = element_line(colour="darkgray"), 
        panel.grid.major.y = element_line(color = 'darkgray'), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        rect = element_blank()
      ) 
```


#### Current Forest Health Incidence

`r htmltopdf(curfhtext())`

```{r, fig.width=8,echo=FALSE,warning=FALSE, message = FALSE}
curfhplot() + theme_bw(12) +
    theme(
      axis.line = element_line(colour="darkgray"), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
      panel.grid.major.y = element_line(color = 'darkgray'), 
      #panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      rect = element_blank(),
      legend.box.background = element_rect(fill = "white", color = "lightgray"),
      legend.position = "none",
      legend.title = element_blank(),
      plot.caption = element_text(hjust=0, size=rel(1.2))
    )  
```

```{r, fig.width=5,fig.height=3,echo=FALSE,warning=FALSE, message = FALSE}
sevplot() + theme_bw(12) +
    theme(
      axis.line = element_line(colour="darkgray"), 
      panel.grid.major.y = element_line(color = 'darkgray'), 
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      rect = element_blank(),
      legend.position = "inside",
      legend.position.inside = c(0.85, 0.85),
      legend.box.background = element_rect(fill = "white", color = NA),
      plot.caption = element_text(hjust=0, size=rel(1.2))
    ) 
```


#### Change in Forest Health Incidence

`r htmltopdf(fhcoctext1())`

```{r, fig.width=8,echo=FALSE,warning=FALSE, message = FALSE}
cocfhplot()  + theme_bw(12) +
      theme(
        axis.line = element_line(colour="darkgray"), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.major.y = element_line(color = 'darkgray'), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        rect = element_blank(),
        legend.box.background = element_rect(fill = "white", color = "lightgray"),
        legend.position = c(0.9, 0.8),
        legend.title = element_blank(),
        plot.caption = element_text(hjust=0, size=rel(1.2))
      ) 
```

`r htmltopdf(fhcoctext2())`

```{r, echo=FALSE,warning=FALSE, message = FALSE, message = FALSE}
fhcocflex()
```


## General Notes

### Disclaimer

`r htmltopdf(disclaimer())`


## Tree Species and Damage Agents Recorded from Mature Samples in `r title()`

:::::::::::::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px; "}
::: {}
#### Tree Species Codes / Names
```{r, include=T, echo=F, warning=FALSE, message = FALSE, message = FALSE}
if (input$format == "HTML"){
    datatable(spcdtab(), rownames= FALSE)
    } else {
      kable(spcdtab())
      }
```
:::

::: {}
#### Damage Agent Codes / Names
```{r, include=T, echo=F, warning=FALSE, message = FALSE}
if (input$format == "HTML"){
    datatable(damcdtab(), rownames= FALSE)
    } else {
      kable(damcdtab())
      }
```
:::
::::::::::::::

```{r, echo=FALSE,warning=FALSE, message = FALSE}
damsevtable()
```


## Reference

`r htmltopdf(ref())`







