---
title: "`r title()` Mature Inventory Assessment"
author: "Forest Analysis and Inventory Branch"
date: "Version 2025-07-15; Created `r Sys.Date()`"
#runtime: shiny
always_allow_html: true
geometry: margin=1cm
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    toc: true
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::opts_chunk$set(fig.height = 4, collapse = TRUE)
knitr::opts_chunk$set(dev = "ragg_png")
set_flextable_defaults(fonts_ignore=TRUE)

htmltopdf <-function(x) {
  if (input$format == "HTML"){
    x
    } else {
      pandoc::pandoc_convert(text = x, from = "html", to = "markdown")
      }
}

colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

library(shiny)
```

<style>
.leaflet {
    margin: auto;
}
</style>


## Overview

#### Overview

`r htmltopdf(description())`

<br>

```{r samplemap, fig.width=8, echo=FALSE, fig.align='center'}
samplemap()
```
<br>

| **Figure 1. Overview map of `r title()`, with ground sample plot locations colour-coded by sample design. The PHASE2 sample design plot locations are the actual spatial coordinates while the GRID sample design plots are generalized to the nearest 1*1km BC Albers grid location in the overview map.**
  
<br>

```{r, include=T, echo=F,warning=FALSE, message = FALSE}
samplenum()
```

<br>
```{r, fig.width=8, echo=FALSE, fig.align='center'}
becplot() + theme_bw(12) +
      theme(
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_line(colour="darkgray")
      )
```


#### Summary of Key Results
<br>

```{r samplesize, echo=FALSE,warning=FALSE, message = FALSE}
samplesize()
```

<br>

::: columns
::: column

```{r, include=T, echo=F,warning=FALSE, message = FALSE}
correct_sp_lead()
```
:::

::: column

```{r, include=T, echo=F,warning=FALSE, message = FALSE}
corsp_vol_flex()
```
:::
:::

<br>
  
| **Listing of those Attributes where Ground: Inventory ratio of means are practically different (Y) or not practically different (N) from 1.0. Attributes which are not listed here have inconclusive (I) results.**

<br>

```{r, include=T, fig.width=8,echo=F,warning=FALSE}
fig2() + theme_bw(12) +
      theme(
         plot.caption = element_text(hjust = 0, size=10, face = "bold"),
      plot.caption.position = "plot",
      legend.position = "top",
      legend.title = NULL,
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank(),
      #panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      axis.text.y = element_blank(), axis.ticks.x = element_blank()
      ) 
```


| **Figure 2. Overall Ratio of means (ground/inventory), 95% confidence interval, & ROPE* interval for the live attributes age, height, basal area & volume, across each sample design.**

<br>
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
test1()

test2()

test3()
```

| *For those strata with a least 8 observations, a region of practical equivalence (ROPE) is pre-determined at 0.9-1.1 to assess if there is a practical difference with the attribute assessed. A practical difference (Y) occurs when the ratio-of-means (ROM) confidence interval (CI) sits entirely outside the ROPE, no practical difference (N) occurs when the ROM CI is entirely within the ROPE, all other situations are inconclusive (I).


```{r, include=FALSE}
incProgress(1/3)
#Sys.sleep(2)
```

## Ground vs. Inventory

#### Stand Summaries

`r htmltopdf(description())`

<br>

```{r, include=T, fig.height=8,echo=F,warning=FALSE}
table1()

table2()

table3()

table4()
```


#### Species Composition

`r htmltopdf(spcomp_text())`

```{r, fig.height=4,echo=FALSE,warning=FALSE}
ld_table1() %>% bg(j = (1:(ld_table1()$body$content$ncol/2))*2, 
                     bg = "lightgray", part = "body")

ld_table2() %>% bg(j = (1:(ld_table2()$body$content$ncol/2))*2, 
                     bg = "lightgray", part = "body")

```


```{r, fig.height=4,echo=FALSE,warning=FALSE}
fig4() + theme_bw(12) +
    theme(
      panel.grid.major.y = element_line(color = 'darkgray'), 
      plot.caption = element_text(hjust=0, size=rel(1.2)),
      legend.position="top",
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )  
```

| **Figure 4. Overall live standing species composition (% of total live merch volume reported in Table 3) between ground and inventory, for both GRID (left) and PHASE 2 (right) sample designs. Species percent is computed from the summed live merch volume (m3/ha) by species of all plots combined. Species composition overlap is a rough index, and expressed as the ratio between the minimum in common relative to the maximum in common that could have been.**
  
```{r, fig.height=4,echo=FALSE,warning=FALSE}
fig5() + theme_bw(12) +
    theme(
      panel.grid.major.y = element_line(color = 'darkgray'), 
      plot.caption = element_text(hjust=0, size=rel(1.2)),
      legend.position="top",
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )  

```

| **Figure 5. Overall dead standing species composition (% of total dead merch volume reported in Table 4) of ground samples, for both GRID (left) and PHASE 2 (right) sample designs. Species percent is computed from the summed dead merch volume (m3/ha) by species of all plots combined. The inventory dead volume is modeled primarily as Mountain Pine Beetle mortality, and therefore assumed 100% allocated to PL.**
  
  
<br>

#### BA, Age, Height, and Volume

```{r, fig.height=10,echo=FALSE,warning=FALSE}
fig6() + theme_bw(12) +
    theme(
       strip.background.x = element_rect(fill=NA, colour=NA,size=1)
    )  

```


| **Figure 6. Scatter plots of ground to inventory age (top), height (middle), and volume (bottom), for GRID samples (left) and PHASE2 samples (right), colour-themed by inventory leading species group. Each graph also includes overlays of the computed ratio of means (red line) and 1:1 reference (grey line).**
  
  

## Compariosn with TSR

#### Current Volumes 

`r htmltopdf(curvoltext())`

```{r, fig.height=4,echo=FALSE,warning=FALSE}
maturetsr() + theme_bw(12) +
    #theme_bw() + 
    theme(
      plot.title = element_text(lineheight = 0.9),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.y = element_line(color = 'darkgray'), 
      rect = element_blank()
    ) 

vol_bias() + theme_bw(12) +
    #theme_bw() + 
    theme(
      legend.position="top",
      #panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_line(color = 'darkgray'), 
      panel.grid.minor.y = element_line(color = 'darkgray'), 
      panel.grid.minor.x = element_blank(),
      rect = element_blank()
    ) 
```
  
#### Periodic Annual Increment

`r htmltopdf(paitext())`

::: columns
::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
tsr_pai_flex1()
```
:::

::: column
```{r, include=T, echo=F, warning=FALSE, message = FALSE}
tsr_pai_flex2()
```
:::
:::

```{r, fig.height=2.5, fig.width=6, echo=FALSE, warning=FALSE, message = FALSE}
paidiff() + theme_bw(12) +
      theme(
        legend.position = "left",
        axis.ticks = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks.x = element_blank(),
        rect = element_blank()
      ) 
```



## Standards of Data Collection

#### VRI Standard

`r htmltopdf(stdcode_text())`

```{r, fig.height=2,echo=FALSE,warning=FALSE}
fig7() + theme_bw(12) + 
    theme(legend.title = NULL,
          rect = element_blank(),
          panel.grid.major.y = element_blank(),
          plot.caption = element_text(hjust = 0, size=10, face = "bold"),
          plot.caption.position = "plot")
```


```{r, include=FALSE}
incProgress(1/3)
#Sys.sleep(2)
```


## Wildfire Impact

#### Ground Samples Impacted by Recent Wildfires

`r htmltopdf(fire_text())`

```{r, fig.width=5, fig.height=3,echo=FALSE,warning=FALSE, message = FALSE}
fig8() + theme_bw(12) + 
      theme(rect = element_blank(),
            panel.grid.minor.y = element_blank(),
            panel.grid.major.x = element_blank(),
            panel.grid.minor.x = element_blank(),
            plot.caption = element_text(hjust = 0, size=10, face = "bold"),
            plot.caption.position = "plot")
```

```{r firemap, fig.width=8, echo=FALSE, fig.align='center'}
if(nrow(firesample()) > 0){
firemap()
}
```


## Forest Health

#### Growth and Mortality

`r htmltopdf(coctext())`

```{r, fig.height=4,echo=FALSE,warning=FALSE, message = FALSE}
cocfig() + theme_bw(12) +
      theme(
        axis.title.y = element_text(color="steelblue"),
        axis.title.y.right = element_text(colour = "#B4464B"),
        legend.box.background = element_rect(fill = "white", color = NA),
        legend.position = c(0.15, 0.85),
        legend.title = element_blank(),
        axis.line = element_line(colour="darkgray"), 
        panel.grid.major.y = element_line(color = 'darkgray'), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        rect = element_blank()
      ) 
```


#### Current Forest Health Incidence

`r htmltopdf(curfhtext())`

```{r, fig.width=8,echo=FALSE,warning=FALSE, message = FALSE}
curfhplot() + theme_bw(12) +
    theme(
      axis.line = element_line(colour="darkgray"), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
      panel.grid.major.y = element_line(color = 'darkgray'), 
      #panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      rect = element_blank(),
      legend.box.background = element_rect(fill = "white", color = "lightgray"),
      legend.position = "none",
      legend.title = element_blank(),
      plot.caption = element_text(hjust=0, size=rel(1.2))
    )  
```

```{r, fig.width=5,fig.height=3,echo=FALSE,warning=FALSE, message = FALSE}
sevplot() + theme_bw(12) +
    theme(
      axis.line = element_line(colour="darkgray"), 
      panel.grid.major.y = element_line(color = 'darkgray'), 
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      rect = element_blank(),
      legend.position = "inside",
      legend.position.inside = c(0.85, 0.85),
      legend.box.background = element_rect(fill = "white", color = NA),
      plot.caption = element_text(hjust=0, size=rel(1.2))
    ) 
```


#### Change in Forest Health Incidence

`r htmltopdf(fhcoctext1())`

```{r, fig.width=8,echo=FALSE,warning=FALSE, message = FALSE}
cocfhplot()  + theme_bw(12) +
      theme(
        axis.line = element_line(colour="darkgray"), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.major.y = element_line(color = 'darkgray'), 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        rect = element_blank(),
        legend.box.background = element_rect(fill = "white", color = "lightgray"),
        legend.position = c(0.9, 0.8),
        legend.title = element_blank(),
        plot.caption = element_text(hjust=0, size=rel(1.2))
      ) 
```

`r htmltopdf(fhcoctext2())`

```{r, echo=FALSE,warning=FALSE, message = FALSE, message = FALSE}
fhcocflex()
```


## Comparison with VDYP

#### Current Volume

`r htmltopdf(growth_text())`

```{r, fig.width=6,include=T, echo=F,warning=FALSE, message = FALSE}
fig7_5()
```

#### Periodic Annual Increment

`r htmltopdf(pai_text())`

::: columns
::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
pai_table1()
```
:::

::: column
```{r, include=T, echo=F, warning=FALSE, message = FALSE}
pai_table1()
```
:::
:::

```{r, fig.height=2.5, fig.width=6, echo=FALSE, warning=FALSE, message = FALSE}
paidiff() + theme_bw(12) +
      theme(
        legend.position = "left",
        axis.ticks = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks.x = element_blank(),
        rect = element_blank()
      ) 
```


## Componets of Bias

#### Model vs. Attribute Bias

`r htmltopdf(bias_comp())`

```{r, fig.width=8,fig.height=3, echo=FALSE,warning=FALSE, message = FALSE}
fig3() + theme_bw(12) +
      theme(
        legend.position = "top",
          axis.ticks = element_blank(),
          axis.text.y = element_blank(),
          panel.grid.major.y = element_blank(),
          #panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          strip.placement = "outside"
      ) 

```

::: columns
::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
fig3_1()
```
:::

::: column
```{r, include=T, echo=F,warning=FALSE, message = FALSE}
fig3_2()
```
:::
:::


| **Figure 3. Components of Bias (total, model, attribute), for Basal Area (left graph) and Volume (right graph), by ground sample design.**


## General Notes

### Disclaimer

`r htmltopdf(disclaimer())`


## Tree Species and Damage Agents Recorded from Mature Samples in `r title()`

:::::::::::::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px; "}
::: {}
#### Tree Species Codes / Names
```{r, include=T, echo=F, warning=FALSE, message = FALSE, message = FALSE}
if (input$format == "HTML"){
    datatable(spcdtab(), rownames= FALSE)
    } else {
      kable(spcdtab())
      }
```
:::

::: {}
#### Damage Agent Codes / Names
```{r, include=T, echo=F, warning=FALSE, message = FALSE}
if (input$format == "HTML"){
    datatable(damcdtab(), rownames= FALSE)
    } else {
      kable(damcdtab())
      }
```
:::
::::::::::::::

```{r, echo=FALSE,warning=FALSE, message = FALSE}
damsevtable()
```


## Reference

#### Reference for Analyses of Past VRI Phase II / VPIP Projects:

```{r, echo=FALSE,warning=FALSE, message = FALSE}
#ref1 <- reference %>%
#  filter(NAME == input$SelectVar) %>%
#  pull(REFERENCE)

DT::datatable(reference, escape = FALSE)
```

```{r, include=FALSE}
incProgress(1/3)
#Sys.sleep(2)
```




